Bootstrap Confidence Intervals for Regression Discontinuity Designs with Uniform Kernels

### 2016-02-23 main_paper.tex
Rewrite first theoretical result and add high-level proof
This commit changes the first bias correction result. Instead of
proving that Delta* is consistent at the 'right' rate, we just
show that the first-stage bias corrected estimator has the same
asymptotic distribution as CCT's bias corrected estimator.

\begin{lemma}\label{L1}
  Under Assumptions~\ref{A1} and~\ref{A3},
  $\Delta^* = \E \hat\tau - \tau + o_p()$.
\end{lemma}

@@

\begin{theorem}\label{T1}
  Let $\Pr_\tau$ represent the probability distribution of the random variables
  under the assumption that $\tau$ is the true value of the ATE and suppose
  Assumptions~\ref{A1} and~\ref{A3} hold. Then
  \begin{equation}
    \label{eq:5}
    \plim_{n \to \infty} \sup_\tau
    \Pr_\tau[\hat\ell(\alpha) \leq \tau \leq \hat u(\alpha)] \geq 1 - \alpha.
  \end{equation}
  Both of the one-sided intervals are asymptotically valid under the same
  assumptions as well:
  \begin{align}
    \plim_{n \to \infty} \sup_\tau
    \Pr_\tau[\hat\ell(\alpha) \leq \tau ] &\geq 1 - \alpha / 2, &
    \plim_{n \to \infty} \sup_\tau
    \Pr_\tau[\tau \leq \hat u(\alpha)] &\geq 1 - \alpha / 2.
  \end{align}
\end{theorem}

@@

>>>>

\begin{theorem}\label{T1}
  Under Assumptions~\ref{A1} and~\ref{A3},
  $(\hat\tau(h_n,b_n) - \Delta^*(h_n,b_n) - \tau) / V^{1/2}(h_n, b_n) \to^d N(0,1)$.
\end{theorem}

@@

\begin{theorem}\label{T2}
  Let $\Pr_\tau$ represent the probability distribution of the random variables
  under the assumption that $\tau$ is the true value of the ATE and suppose
  Assumptions~\ref{A1} and~\ref{A3} hold. Then
  \begin{equation}
    \label{eq:5}
    \plim_{n \to \infty} \sup_\tau
    \Pr_\tau[\hat\ell(\alpha) \leq \tau \leq \hat u(\alpha)] \geq 1 - \alpha.
  \end{equation}
  Both of the one-sided intervals are asymptotically valid under the same
  assumptions as well:
  \begin{align}
    \plim_{n \to \infty} \sup_\tau
    \Pr_\tau[\hat\ell(\alpha) \leq \tau ] &\geq 1 - \alpha / 2, &
    \plim_{n \to \infty} \sup_\tau
    \Pr_\tau[\tau \leq \hat u(\alpha)] &\geq 1 - \alpha / 2.
  \end{align}
\end{theorem}

@@

\appendix
\section{Mathematical Appendix}
\subsection{Proof of Theorem~\ref{T1}}
We have
\begin{equation*}
  \hat\tau - \Delta^* - \tau = (\hat\tau - \E \hat \tau) +
  (\E \hat \tau - \tau) - (\E^* \hat \tau^* - \tau^*)
\end{equation*}

The design of the bootstrap ensures that
\begin{equation*}
  \label{eq:7}
  \E^* \hat\mu_{\pm}^*(h) - \mu_{\pm}^{*} = h^{2} \mu_\pm^{*(2)} \Bf_{\pm}(h)/2,
\end{equation*}
almost surely, implying that
\begin{equation*}
  \label{eq:20}
    \E^* \hat\tau^{*} - \tau^{*} = h_n^2\, \mu_+^{*(2)} \Bf(h_n)/2
      - h_n^2\, \mu_{-}^{*(2)} \Bf_{-}(h_n)/2.
\end{equation*}
Combining this result with CCT's Lemma A1, gives
\begin{align*}
  \hat\tau &- \E \hat\tau + (\E \hat\tau - \tau) - (\E^* \hat\tau^* - \tau^*)\\
  &= \hat\tau - \E\hat\tau
   + h_n^2 \big((\mu_{-}^{*(2)} - \mu_{-}^{(2)}) \Bf_{-}(h_{n}) /2
   - (\mu_+^{*(2)}-\mu_+^{(2)}) \Bf_{+}(h_{n}) / 2 \big) + O_p(h_n^{3}) \\
  &= \hat\tau - \E\hat\tau
   + h_n^2 (\hat\mu_-^{(2)}(b_n) - \mu_-^{(2)}) \Bf_{-}(h_{n}) /2
   - h_n^2 (\hat\mu_+^{(2)}(b_n) - \mu_+^{(2)}) \Bf_{+}(h_{n}) / 2 + O_p(h_n^{3})
\end{align*}
The second equality holds because
$\mu_\pm^{*(2)} = \hat\mu_{\pm}^{(2)}(b_n)$ a.s. Asymptotic normality then
follows from normality of $\hat\tau - \E\hat\tau$ and
$\hat\mu_\pm^{(2)}(b_n) - \mu_\pm^{(2)}$ using
similar arguments to CCT's Lemma SA4.D.\qed
